### 2014-03-16 src/introduction.Rnw
Fix spellos

One of the impediments to wider adoption of mutation analysis is its
high computational cost.  The set of simple mutants for even a
moderate sized program can be very large, making mutation
analysis prohibitivey time consuming.

@@

Selective mutation strategies attempt to select a representative
subset of mutation \emph{operators} based on heuristics and
statistical analysis, and apply this subset of operators to generate
mutants instead of applying the whole set of mutation
operators~\cite{offutt1993anexperimental,untch2009onreduced}.
Recent work suggests that using statement deletion only can
be effective~\cite{untch2009onreduced}.

@@

%Mathur \cite{} reduced the number of mutagens in Mothra \cite{Mothra} by omitting two operators.
%Offutt et al.\cite{offutt1993anexperimental} further omitted upto six oprators from the
%mutagens and observed negligible loss of effectiveness in mutation analysis.
%Unch\cite{untch2009onreduced} and more recently Deng et al.\cite{deng2013empirical} suggest
%that using only statement deletion operator gives a close approximation of original mutation score.

%While some studies try to
%find the \emph{sufficient} subset of mutagens, like\cite{siami2008sufficient}, others
%have suggested that \emph{random} selection of mutants works as fine, e.g. \cite{zhang2010operator}.
%Some approaches combine the selective mutation selection and random selection, e.g. \cite{zhang2013ase}.

% {Amin: I am not a fan of this ~\cite{hussain08mutation} }
%Finally, clustering of mutants~\cite{hussain08mutation} based on similar test cases has also
%been used successfully for mutant reduction. These are explained more in depth in Section~\ref{sec:related}

Recent work~\cite{zhang2010icse,zhang2013ase} has investigated the
relative merits of random sampling strategies and operator selection.
Random sampling can perform as well as or better than operator
selection, in these studies; a strategy of either sampling based on
program elements or one combining both program element-based sampling
and operator selection was best.

However, as pointed out by Zhang et al.~\cite{zhang2013ase}, the field
has a serious lacuna in large scale research, both in the size of the
programs studied, and in the number and diversity of programs, which
reduces our confidence in all results. This is true for selective
mutation studies, studies in sampling, and also for comparatively
newer studies that attempt to combine methods. This is particularly
worrisome if mutation analysis is to gain wider acceptance among
testing professionals. Further, quite a few of the influential
studies~\cite{offutt1993experimental,offutt1996anexperimental,wong1995reducing,mresa1999efficiency}
were conducted on older programming languages such as Fortran, with
operators specific to the language, and are not directly applicable to
newer languages such as Java. Finally, due to modern research into the byte
code based mutation (a \textit{do faster} approach for eliminating
the compilation step to gain execution speed), operators based on
source code modification are no longer applicable, and their
equivalents in bytecode need to be identified and compared with other
approaches. A detailed discussion of these issues can be found in
Section~\ref{sec:related}.

@@

%The research concludes in Section~\ref{sec:conclusion}.

@@

\item We compare a much large number of mutant reduction strategies
than previous studies. We compare with respect to the predictive power
(correlation) with the full mutation score, expected mutant reduction,
and the stability of the amount of mutant reduction expected. Our
sampling strategies include some that were suggested by other
researchers, as well as a few novel strategies not previously considered.

@@

%We make the following contributions:
%\begin{itemize}
%\item We compare a large number of mutation sampling and selection strategies (Section~\ref{sec:analysis}).
%\item It seek sto improve the statistical confidence in our results by utilizing a much larger sample of projects
%      (188 projects) from the open source repository at Github~\cite{github}, using both original and automatically
%      generated test suites using Randoop~\cite{randoop} (Section~\ref{sec:methodology}). 
%\item It analyses the results and suggest strategies (Section~\ref{sec:results}).
%\end{itemize}

%Our contributions in this paper are the following. First, as described in Section~\ref{sec:methodo%logy},
%we seek to improve the statistical confidence in our results by utilizing a much larger sample of projects
%(188 projects) from the open source repository at Github~\cite{github}, using both original and automatically
%generated test suites using Randoop~\cite{randoop}. Second, as detailed in Section~\ref{sec:analysis}, we
%compare the reduction effectiveness of a large number of random sampling criterias (some of which are novel,
%and some that has been proposed by other researchers), and a some of the common operator selection
%criterias proposed in literature using statistical analysis. This provides us with insight for choosing
%mutation reduction techniqus according to the trade-offs in accuracy, and reduction ratios that a tester
%is willing to make for their specific requirements. This is detailed in Section~\ref{sec:results}.

%Our conclusion and recommendation for practicing testers are provided in Section~\ref{sec:conclusion}.

% \begin{comment}
% Order of most fertile operators for N-selective operator selection.
% NON_VOID_METHOD_CALLS
% NEGATE_CONDITIONALS
% REMOVE_CONDITIONALS
% DELETE_CONDITIONALS
% RETURN_VALS
% INLINE_CONSTS
% CONSTRUCTOR_CALLS
% EXPERIMENTAL_MEMBER_VARIABLE
% VOID_METHOD_CALLS
% MATH
% CONDITIONALS_BOUNDARY
% INCREMENTS
% REMOVE_INCREMENTS
% RMSWITCH
% EXPERIMENTAL_SWITCH
% INVERT_NEGS
%
% \end{comment}
%
% NON_VOID_METHOD_CALLS VOID_METHOD_CALLS CONSTRUCTOR_CALLS
% NEGATE_CONDITIONALS REMOVE_CONDITIONALS DELETE_CONDITIONALS CONDITIONALS_BOUNDARY
% RETURN_VALS INLINE_CONSTS EXPERIMENTAL_MEMBER_VARIABLE
% MATH INCREMENTS REMOVE_INCREMENTS INVERT_NEGS
% RMSWITCH EXPERIMENTAL_SWITCH

>>>>

One of the impediments to wider adoption of mutation analysis is its
high computational cost.  The set of simple mutants for even a
moderate sized program can be very large, making mutation
analysis prohibitively time consuming.

@@

Selective mutation strategies attempt to select a representative
subset of mutation \emph{operators} based on heuristics and
statistical analysis, and apply this subset of operators to generate
mutants instead of applying the whole set of mutation
operators~\cite{offutt1993anexperimental,untch2009onreduced}.
Recent work suggests that using statement deletion alone can
be an effective approach~\cite{untch2009onreduced}.

@@

Recent work~\cite{zhang2010icse,zhang2013ase} has investigated the
relative merits of random sampling strategies and operator selection.
Random sampling can perform as well as or better than operator
selection, in these studies; and a strategy of either sampling based on
program elements or one combining both program element-based sampling
and operator selection was best.

However, as pointed out by Zhang et al.~\cite{zhang2013ase}, the field
has a serious lacuna in large scale research, both in the size of the
programs studied, and in the number and diversity of programs, which
reduces our confidence in all results. This is true for selective
mutation studies, studies in sampling, and also for comparatively
newer studies that attempt to combine methods. This is particularly
worrisome if mutation analysis is to gain wider acceptance among
testing professionals. Further, quite a few of the influential
studies~\cite{offutt1993experimental,offutt1996anexperimental,wong1995reducing,mresa1999efficiency}
were conducted on older programming languages such as Fortran, with
operators specific to the language, and are not directly applicable to
newer languages such as Java. Finally, with bytecode based mutation
engines like PIT~\cite{pitest} and Javalanche~\cite{javalanche}
(a \textit{do faster} approach for eliminating
the compilation step to gain execution speed), operators based on
source code modification are no longer applicable, and their
equivalents in bytecode need to be identified and compared with other
approaches. A detailed discussion of these issues can be found in
Section~\ref{sec:related}.

@@

@@

\item We compare a much large number of mutant reduction strategies
than previous studies. We compare with respect to the predictive power
(correlation with the full mutation score), expected mutant reduction,
and the stability of the amount of mutant reduction expected. Our
sampling strategies include some that were suggested by other
researchers, as well as a few novel strategies not previously considered.

@@
